%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-234-5678 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jin Huang} \\ \vspace{1pt}
    \small 213-399-4359 $|$ \href{mailto:jinhuang922@gmail.com}{\underline{jinhuang922@gmail.com}} $|$ 
    \href{https://scholar.google.com/citations?user=V9IzEq8AAAAJ&hl=en}{\underline{Google Scholar}} $|$
    \href{https://github.com/JinHuang0101}{\underline{GitHub}}
    $|$
    U.S. Citizen
    $|$
    Portland, Oregon
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR}
      {Bachelor of Science in Computer Science, GPA: 3.92}{Aug. 2020 -- Expct. Dec. 2024}
    \resumeSubheading
      {University of Southern California}{Los Angeles, CA}
      {Ph.D., M.A. in Communication and Technlogy, Quantitative Social Science}{Sep. 2011 -- May 2018}
    \resumeSubheading
      {Huazhong University of Science \& Technology}{Wuhan, China}
      {Bachelor of Arts in Broadcast and TV Journalism}{Sep. 2004 -- June. 2008}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
     \textbf{Languages}{: Python, SQL, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Express-Node.js, Streamlit} \\
     \textbf{Tools}{: MongoDB, MySQLWorkbench, phpMyAdmin, Github, Google Cloud, VS Code, Jupyter Notebook, Jira} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, seabborn, sklearn}\\
     \textbf{Data Analytics}{: BigQuery, Tableau, PowerBI, Excel, SPSS}\\
     \textbf{Statistics}{: Hypothesis Testing, Natural Language Processing, Regression, Exploratory Data Analysis, Sampling}\\
     \textbf{Research Methods}{: Survey, Interview, Focus Group, Content Analysis}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI Tools Online Marketplace} $|$ \emph{JavaScript, Express-Node.js, SQL, HTML/CSS, server, Github}}{Sep.2023 -- Present}
          \resumeItemListStart
            \resumeItem{\textbf{Captain and sole backend \& database developer} of a team of two}
            \resumeItem{Developed a full-stack web application with HTML/CSS for the frontend and used Express-Node.js to serve a REST API that allows database administrators to perform CRUD operations on the database via a UI}
            \resumeItem{Used AJAX and Handlebars to dynamically display data from a MySQL database on the frontend page}
            \resumeItem{Designed and built a MySQL relational database with 5 entities and 2 intersection tables}
            \resumeItem{Deployed the frontend, backend, and database to the university's remote server}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Stock Galaxy, Pick a Star} $|$ \emph{Python, Streamlit, pandas, matplotlib, prompt engineering}}{Sep. 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Built a full-stack web app to retrieve 10 key financial metrics from the 10-K data of all 10726 SEC-listed companies using the SEC EDGAR API}
            \resumeItem{Used pandas DataFrame and Python dictionary data structures, and sorting algorithms to sort and rank stocks based on various financial metrics}
            \resumeItem{Integrated a chatbot, powered by OpenAI, into the web app to answer user questions}
            \resumeItem{No skeleton code, no hardcoded strings; implemented error handling in Python. The program is fully automated, scalable to handle large-scale data, and includes data visualization}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Female Tech Entrepreneur} $|$ \emph{Python, JavaScript, HTML/CSS, prompt engineering}}{Oct. 2023}
          \resumeItemListStart
            \resumeItem{Built an AI Agent and a Google Chrome extension using the OpenAI engine for the Major League Hacking Open Source Week}
            \resumeItem{Published the agent to the AI Agent Community, where it ranked as the \#3 most popular among 2,714 submissions and remained on the most popular page for two weeks}
          \resumeItemListEnd  
      \resumeProjectHeading
          {\textbf{Exercise Tracker} $|$ \emph{JavaScript, HTML/CSS, React, Express-Node.js, MongoDB}}{Present}
          \resumeItemListStart
            \resumeItem{Built a full-stack web app using Express-Node.js to serve a REST API, with React for the front-end, and MongoDB as a NoSQL database}
            \resumeItem{Enabled users to perform CRUD operations on the database, allowing them to keep track of their exercise records}
            \resumeItem{Deployed the full-stack web app to Netlify for hosting}
          \resumeItemListEnd
      \resumeProjectHeading 
          {\textbf{Kuba Game} $|$ \emph{Python}}{Present}
          \resumeItemListStart
            \resumeItem{Built a Command Line Interface program to play Kuba Game uing Object-Oriented Programming design principles without any skeleton code}
            \resumeItem{Implemented unit testings to verify gameplay functionality}
          \resumeItemListEnd    

    \resumeSubHeadingListEnd

%-----------ACADEMIC APPOINTMENTS-----------
\section{Academic Appointments}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Project Manager}{2016 -- 2018}
      {International Journal of Communication}{ University of Southern California}
      \resumeItemListStart
        \resumeItem{Ranked \# 8 among social science journals}
        \resumeItem{Leader of a team of 10 editorial assistants, managed tasks and deadlines, ensured quality control, conducted scientific paper reviews, and collaborated with 130+ editorial members and 1000+ social scientists in the field of human-computer interaction}
      \resumeItemListEnd

    \resumeSubheading
      {Editorial Assistant}{2014 -- 2016}
      {International Journal of Communication}{ University of Southern California}
      \resumeItemListStart
        \resumeItem{Conducted a weekly review of original research manuscripts, assessing their content, validity, and adherence to publication standards}
      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{2012 -- 2014}
      {Annenberg School for Communication \& Journalism}{ University of Southern California}
      \resumeItemListStart
        \resumeItem{Project: Developing Communication Network Skills through Penny Harvest}
        \resumeItem{Project: Value Pursuit in Crowdfunding on Kickstarter}
        \resumeItem{Project: Local Storytelling and Civic Engagement in the City of Alhambra, Los Angeles}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{2012 -- 2014}
      {Annenberg School for Communication \& Journalism}{ University of Southern California}
      \resumeItemListStart
        \resumeItem{Course: Communication, Attitudes and Behaviors (Graduate core, seminar)}
        \resumeItem{Course: Communication and Mass Media (Undergraduate core, lecture \& discussion)}
        \resumeItem{Course: Communication and Social Science (Undergraduate core, lecture \& discussion)}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Marketing Research Consultant}{June 2010 -- Sep. 2011}
      {Burson Cohen \& Wolfe, WPP plc, \#1 Ad Agency}{Beijing, China}
      \resumeItemListStart
        \resumeItem{Led the design and implementation of the 1st national social media campaign for Lexus China}
        \resumeItem{Published numerous press releases for Lexus, covering corporate communication and product launches}
        \resumeItem{Presented a SWOT analysis to the Vice President of Lexus Asia}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{International \& National Awards}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small
    {\item{
    \textbf{Top Student Paper Award}{ International Communication Association (Public Relations), Puerto Rico, 2015}
    }}
    {\item{
    \textbf{Top Faculty Paper Award}{ International Communication Association (Public Relations), Puerto Rico, 2015}
    }}
    {\item{
    \textbf{Top Faculty Paper Award}{ National Communication Association (Argumentation and Forensics), Chicago, 2014}
    }}
  \end{itemize}  

%-----------Scholarships-----------
\section{University Scholarships}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small 
    {\item{
    Graduate Student Scholarship. University of Southern California. 2012-2016
    }}
    {\item{
    Scholar Symposium Awards. University of Southern California. 2014
    }}
    {\item{
    Annenberg Fellow Research Awards. University of Southern California. 2014
    }}
    {\item{
    Graduate Student Fellowship. University of Southern California. 2011-2012
    }}
    {\item{
    National Scholarship for Overseas Exchange Program. University of Southern California. 2007
    }}
    {\item{
    National Scholarship for Excellent University Freshmen. University of Southern California. 2004 
    }}
    {\item{}}

 \end{itemize}    

%-----------PUBLICATIONS-----------
\section{Publications}
 \begin{itemize}[leftmargin=0.15in, label={}]
   \small
   {\item{
     Goodnight, G.T., Son, M., \textbf{Huang, J.}, \& Crigler, A. (2017). Youth, networks, and civic engagement: Communities of belonging and communities of practice. Speech and Debate as Civic Education, 205-220.
    }}
    {\item{
    \textbf{Huang, J. } (2015). Raising the standing of evaluation in dialogic research: The influence of budget and evaluation style on dialogue implementation. Top Student Paper Award. International Communication Association. Puerto Rico. 
    }}
    {\item{
    \textbf{Huang, J.}, \& Yang, A. (2015). Implementing dialogic communication: A survey of IPR, PRSA, and IABC members. Public Relations Review. 41(3), 376-377. [5-Year Impact Factor=2.086]
    }}
    {\item{
    \textbf{Huang, J.}, \& Yang, A. (2015). Understanding factors affecting organizations’ implementation of dialogic communication: An exploratory study. Top Faculty Paper Award. International Communication Association. Puerto Rico. 
    }}
    {\item{
    Goodnight, G.T., Son, M., \& \textbf{Huang, J.} (2014). Youth, networks and civic engagement: An interim report. Top Faculty Paper Award. The National Communication Association. Chicago. 
    }}
    {\item{
    \textbf{Huang, J.} (2014). The sweetness of solitude in SNS: An integrative model on online privacy, withdrawal, and self-disclosure. International Communication Asociation. Seattle. 
    }}
    {\item{
    Chen, N.T.N., Dong, F., Ball-Rokeach, S.J., Parks, M., \& \textbf{Huang, J.} (2012). Building a new media platform for local storytelling and civic engagement in ethnically diverse neighborhoods. New Media \& Society, 14(6), 931-950. [5-Year Impact Factor=4.18]
    }}
    {\item{
    \textbf{Huang, J.} (2012). The social influences of Facebook friends. InfoSocial Conference. Evanston, IL. 
    }}
    {\item{
    Chen, N.T.N., Ball-Rokeach, S.J., Parks, M., \& \textbf{Huang, J.} (2011). The Alhambra project: A theory-based strategy for the construction of a citizen journalism website. Centres and peripheries: Metropolitan and non-metropolitan journalism in the twenty first century, 255-270. 
    }}
    {\item{
    Chen, N., \& \textbf{Huang, J.} (2009). The Alhambra project: Building a civically engaged community through the re-localization of news in Alhambra, Los Angeles County. The National Communication Association. Chicago. 
    }}
    {\item{
    \textbf{Huang, J.} (2007). Culture elements embedded in the process of European integration. Professional Circle, May 2007.
    }}
 \end{itemize}    

%


%-------------------------------------------
\end{document}
